An exploratory analysis of the influence of resource use on the yield verse quality trade-off in Australian vineyards

### 2023-07-31 article.tex
Added map place holder
Added pearson corr table and ref to it.

Linear relationships between variables were explored using Pearson Correlation Coefficients. Values for these coefficients reflect the linear relation between two variables, on a scale between -1 and 1; the magnitude and sign of a coefficient indicates the strength of the relation, and whether the relation is positive or negative respectively. This was undertaken for data on the original scale (see Table ??) and for data as a logarithmic transform (see Table ??). The logarithmic transformed data showed the strongest correlations, likely due to a skew caused by a greater number of smaller vineyards within the dataset (see Table ??). Transforming data prior to calculating the coefficients changes several things: The logarithmic transform of the data alters the interpretation of the coefficients to percentage change - a coefficient will be indicative of the change in percentage of one variable compared to the other; scaling by standard deviation also changes this interpretation to be a percentage of that variables standard deviation. Scaling by standard deviation also makes the Pearson Correlation Coefficient equal to the covariance of the two variables. With all this in mind, when considering the logarithmically transformed variables, a coefficient of 1 would indicate that: given the change of one variable by one percentage of its standard deviation, the other variable would change by one percent of its own standard deviation. The importance of this is the dimensionless nature of these relationships and that it can be translated directly to any vineyard's case that has a well known distribution.

>>>>

  \caption{Variable Pearson correlation values for logarithmically transformed values.}\label{tab:pearson_correlation}
        \textbf{Variable} & \textbf{Yield} & \textbf{Area Harvested} & \textbf{Water Used} & \textbf{Scope One Emissions} & $\textbf{Yield}\over \textbf{Area}$ & \textbf{Average Sale Price} & $\textbf{Average Sale Price}\over \textbf{Area Harvested}$ \\ \midrule
        \textbf{Yield} & 1.00E+00 & 7.44E-01 & -4.31E-03 & 7.29E-01 & 3.50E-01 & -2.26E-01 & -1.64E-01 \\
        \textbf{Area Harvested} & 7.44E-01 & 1.00E+00 & -5.33E-03 & 8.92E-01 & 7.85E-02 & -1.18E-01 & -2.04E-01 \\
        \textbf{Water Used} & -4.31E-03 & -5.33E-03 & 1.00E+00 & -1.93E-03 & -5.60E-03 & -3.56E-02 & -2.67E-02 \\
        \textbf{Scope One Emissions} & 7.29E-01 & 8.92E-01 & -1.93E-03 & 1.00E+00 & 9.36E-02 & -9.42E-02 & -1.93E-01 \\
        $\textbf{Yield}\over \textbf{Area}$ & 3.50E-01 & 7.85E-02 & -5.60E-03 & 9.36E-02 & 1.00E+00 & -4.85E-01 & -1.70E-01 \\
        \textbf{Average Sale Price} & -2.26E-01 & -1.18E-01 & -3.56E-02 & -9.42E-02 & -4.85E-01 & 1.00E+00 & 4.73E-01 \\
        $\textbf{Average Sale Price} \over \textbf{Area Harvested}$ & -1.64E-01 & -2.04E-01 & -2.67E-02 & -1.93E-01 & -1.70E-01 & 4.73E-01 & 1.00E+00 \\ \bottomrule
Linear relationships between variables were explored using Pearson Correlation Coefficients. Values for these coefficients reflect the linear relation between two variables, on a scale between -1 and 1; the magnitude and sign of a coefficient indicates the strength of the relation, and whether the relation is positive or negative respectively. This was undertaken for data on the original scale and for data as a logarithmic transform. The logarithmic transformed data showed the strongest correlations, likely due to a skew caused by a greater number of smaller vineyards within the dataset (see Table \ref{tab:pearson_correlation}). Transforming data prior to calculating the coefficients changes several things: The logarithmic transform of the data alters the interpretation of the coefficients to percentage change - a coefficient will be indicative of the change in percentage of one variable compared to the other; scaling by standard deviation also changes this interpretation to be a percentage of that variables standard deviation. Scaling by standard deviation also makes the Pearson Correlation Coefficient equal to the covariance of the two variables. With all this in mind, when considering the logarithmically transformed variables, a coefficient of 1 would indicate that: given the change of one variable by one percentage of its standard deviation, the other variable would change by one percent of its own standard deviation. The importance of this is the dimensionless nature of these relationships and that it can be translated directly to any vineyard's case that has a well known distribution.
